### 2017-05-11 paper1.tex
Add files via upload

Thermal infrared (TIR) remote sensing of land surface temperature (T\textsubscript{surf}) has emerged as a primary research focus in climatology, as researchers seek to better describe spatiotemporal patterns of T\textsubscript{surf} globally and better understand how anthropogenic modification of earth's surface influences land T\textsubscript{surf} and impacts climate at various scales. Over the last two decades, the application of thermal remote sensing to study surface climates has expanded significantly. Thermal remote sensing of earth's surface has applications over a wide range of disciplines: from informing micro-, urban-, and global-scale climate models, to aiding decision making and mitigation praxis with respect to climate change and the urban heat island effect.

@@

Although most thermal remote sensors operate within one of the atmospheric windows - where atmospheric effects are minimal - virtually any remote sensed TIR signal is subject to radiative effects from the layer of atmosphere between the surface and the sensor. Over much of the thermal infrared waveband the atmosphere emits radiation and absorbs a fraction of radiation emitted by the surface. Thus, a remote sensed TIR signal is almost certainly not equal to the ground emitted signal. Spectral radiance received by a sensor at height ($z$) can be described by a function deviating from a Planck curve defined by T\textsubscript{surf} based on the spectral transmittance of the intervening atmosphere, with the magnitude of that deviation determined by the difference between Planck curves calculated from T\textsubscript{surf} and ambient T\textsubscript{air}. A radiative transfer code, such as MODTRAN \citep{Berk1987}, can be used to model the effect of the atmosphere on a remote sensed TIR signal. Radiative transfer simulations run in MODTRAN version 4.1 for two path lengths are shown in Figure \ref{spectairtsurf}, for spectral radiance emitted from a planar surface at 300 \si{\kelvin} through an isothermal atmosphere at 290 \si{\kelvin}, water vapor content of 12 \si{\gram\per\meter\cubed}, and aerosol and trace gas profiles from the mid-latitude summer standard atmosphere \citep{Kantor1962}. At both short and long path lengths, radiance in each band shows some deviation from the ground emitted signal. Larger deviations are observed at longer path lengths, where a significant portion of the resulting signal is emitted from that atmosphere, even in bands with high spectral transmittance. Long path lengths and a less transmissive atmosphere increase the potential for deviation in a remote sensed TIR signal from the ground emitted signal, while the difference between T\textsubscript{air} and T\textsubscript{surf} determines the resulting magnitude of atmospheric influence.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{spectairtsurf}
	\caption{At-sensor spectral directional radiances computed in MODTRAN 4.1 (Berk et al., 1987) for short (30 \si{m}) and long (3000 \si{m}) path lengths (z) with Planck curves indicating spectral radiances at T\textsubscript{surf} = 300 \si{K} and T\textsubscript{air} = 290 \si{K}.}
	\label{spectairtsurf}
\end{figure}

@@

Inversions of uncorrected $ L_z $ or \textbf{$L_z'$} yield a temperature equal to that of a blackbody emitting the same amount of radiation as detected by the sensor. Since $ L_z $ is unlikely to be equal to $ L_0 $ and, by extension,  $L_z'$ is unlikely to be equal to $L_0'$, T\textsubscript{hem, b} at $ z = 0 $ and T\textsubscript{hem, b} at $ z $ often show significant deviation based on sensor characteristics, ambient conditions, and surface-sensor geometry. Hence, T\textsubscript{bright} and T\textsubscript{hem, b} are generally considered only a rough approximation representation of radiometric T\textsubscript{surf}.

@@

A large number of correction routines have been developed to remove atmospheric and emissivity effects from aerial and satellite TIR signals and derive accurate T\textsubscript{rad}. Methods range from simple mono-window \citep{Qin2001} and split-window \citep{Wan1996} routines for single-channel and multi-channel remote sensors, to schemes that integrate a radiative transfer code to isolate the surface emitted signal from interfering signals. Boundary conditions are standard across most correction methods: generally requiring vertical profiles of T\textsubscript{air}, humidity, pressure, and aerosol content to remove atmospheric effects, and surface radiative properties to correct for emissivity effects. However, correction methods are often instrument (or, at the very least, least platform) specific and difficult to generalize across sensor and platform types. Few methods exist for correction of ground based remote sensed TIR --- none of which are robust enough to correct irradiances measured from a near-ground wide-field-of-view (FOV) radiometer mounted to view rough terrain.

@@

Several multi-LOS correction routines have been developed to remove atmospheric effects on near-ground remote sensed TIR: \citet{Meier2011} describes a correction method for oblique angled thermal imagery of urban terrain. In the method, spatially distributed LOS geometries were calculated by linking each image pixel to the corresponding 3-d coordinates of its viewpoint on a digital building model (DBM). Path lengths were then calculated as the distance between each pixel's corresponding location on the DBM and the sensor represented as the vanishing point of a 3-dimensional pyramidic projection from the sensor's location in the DBM. A pixel-by-pixel correction was then applied to remove atmospheric effects and retrieve T\textsubscript{rad} for each pixel at 30 minute intervals, resulting in a time-continuous climatology of urban T\textsubscript{rad}. However, the method uses thermal images in conjunction with a DBM to calculate path length geometries for each pixel's LOS - a technique not possible with a pyrgeometer, which returns a single integrated value over the sensor FOV. Moreover, the target instrument operates over a narrow waveband with relatively uniform spectral sensor response, reducing the magnitude and variance in atmospheric transmission over the sensor response curve. Thus, the method is not directly generalizable to correct TIR measured via pyrgeometer.

\citet{Kotani2009a} describes a method for correction of wide-FOV (pyrgeometer) TIR irradiances over a homogeneous planar surface. In this method, path lengths were calculated for six sensor heights. Radiances were then modeled using the LOWTRAN \citep{Kneizys1988} radiative transfer code initialized at $5^{\circ}$ intervals and integrated over the hemisphere to retrieve irradiances for a suite of T\textsubscript{surf}, and ambient T\textsubscript{air} and humidities. The resulting lookup table (LUT) of values is then used to correct $L_z$ and quantify atmospheric effects on remote sensed $L_z$ measured from several sensor heights. Methods outlined in \citet{Meier2011} and \citet{Kotani2009a} are limited to narrow-FOV thermal imagers and planar terrain respectively. A method which combines \citet{Meier2011}'s representation of complex surface geometry and \citep{Kotani2009a}'s broadband hemispherical integration is needed for atmospheric correction of urban TIR measured via downward facing pyrgeometer.

@@

The "rolling lookup-table" method described in this study uses a sensor view model in conjunction with a radiative transfer code to model hemispherical irradiances upwelling from a simplified isothermal 3-dimensional representation of the urban surface. In summary, the method (depicted in Figure \ref{flow}) uses vertical profiles of measured T\textsubscript{air} and humidity to model at-sensor spectral radiances at 5$^{\circ}$ increments over the sensor FOV for a predetermined range of possible T\textsubscript{hem, r} at each time-step. Spectral directional radiances are convolved by a dome transmittance curve, integrated over the sensor waveband, and weighted for their respective angular view factor. Weighted directional radiances are then integrated over the hemisphere and aggregated into a LUT of modeled irradiance - T\textsubscript{hem, r} pairings for each time step, unique to the vertical profile of measured T\textsubscript{air} and humidity. Finally, for each time step, measured irradiances are matched with the closest modeled irradiances in the LUT to return an atmospherically corrected radiometric hemispherical surface temperature. This process is repeated at 30 minute intervals to yield a continuous climatology of urban T\textsubscript{hem, r} for surface urban heat island (sUHI) analysis. The following sections introduce the study area for which the method was developed and describe the sensor view model, radiative transfer, and post-processing steps of the correction method.

@@

With methodological generalizability in mind, a "rolling lookup table" atmospheric correction method was developed to retrieve radiometric T\textsubscript{hem, r} for a climatology of upwelling longwave irradiances measured from above the Sperrstrasse street canyon in Basel, Switzerland. The site, instrumented as a part of the Basel Urban Boundary Layer Experiment (BUBBLE) \cite{Rotach2005}, has an approximately northeast-southwest orientation and site morphology representative of local climate zone (LCZ) 2\footnote{Site surroundings can be described by the following morphological parameters: mean building height: 14.6m, plan aspect ratio: 0.54, complete aspect ratio: 1.92, local canyon aspect ratio: 1.0, and average shortwave albedo: 0.11 \cite{Rotach2005}.} \cite{Stewart2012}. LCZ classification was based on an assessment of surface characteristics in a 250 \si{\meter} circular area extending from the Sperrstrasse tower using a 1 \si{m} raster digital building model (DBM). Thus, the morphological parameters identified in \cite{Rotach2005} are representative of a majority of the pyrgeometer footprint. Vegetation was not included in the DBM, and thus is not represented in morphological assessment or the sensor view model, however, the street canyon and surrounding area has little vegetation.

For the eight month period between December 2001 and July 2002, a triangular lattice tower was installed within the Sperrstrasse street canyon. It's location was skewed towards the southeast facing wall near the along-canyon center of the canyon. Instruments to observe a full suite of meteorological variables and fluxes of heat, mass, and momentum are mounted at various levels on the tower. Profiles of T\textsubscript{air} and humidity were measured at seven heights extending from 2.5 \si{m} to 31.5 \si{m} above the canyon floor (with the highest observation level at approximately 2.17 times mean roof level). Upwelling and downwelling short/longwave fluxes were obtained from radiometers mounted at the lowest and highest measurement levels, with an additional downward facing pyrgeometer mounted at roof level near the center of the street canyon. In addition, during a summertime intensive observation period (IOP) an array of narrow-FOV IRTs was installed to sample representative individual facet surface temperatures (T\textsubscript{facet}).

The BUBBLE Sperrstrasse site was chosen here for two primary reasons: 1. The site provided a long-term climatology of radiation and meteorological variables for a representative mid-latitude city. This allowed for examination of urban T\textsubscript{surf}, sUHI, and atmospheric correction magnitudes over a wide range of representative mid-latitude conditions. 2.  Inclusion of T\textsubscript{facet} over the IOP allows for investigation of the effect of sensor-surface geometry on remote sensed urban T\textsubscript{surf} for common urban T\textsubscript{surf} measurement strategies. This directional dependence of urban T\textsubscript{surf} - termed "effective anisotropy" - refers to the notion that a TIR signal upwelling from rough terrain viewed from a remote sensor changes based on the combined effects of surface-sensor-sun geometry and the convoluted, 3-dimensional structure of the urban surface \cite{Voogt1998a}. Facet surface temperatures measured during the summertime IOP allow for direct climatological comparison of T\textsubscript{hem, r} to common remote sensed representations of the urban surface constructed from weighted averages of wall (T\textsubscript{wall}), road (T\textsubscript{road}), and roof (T\textsubscript{roof}) temperatures. Plan and complete aspect ratios are used to derive weightings for nadir remote sensed (T\textsubscript{plan}) and complete (T\textsubscript{comp}) representations of urban surface temperature - described in Table \ref{weightings}. At each time step, T\textsubscript{hem, r} and T\textsubscript{plan} were divided by T\textsubscript{comp} and averaged over the IOP to yield normalized mean T\textsubscript{hem, r} and T\textsubscript{plan} at 30-minute intervals. Through comparison of T\textsubscript{hem, r} to T\textsubscript{plan} and T\textsubscript{comp} we investigate the effect of sensor-surface geometry on remote sensed urban T\textsubscript{surf} and quantify directional biases in common urban T\textsubscript{surf} measurements.

\begin{table}[H]
	\centering
	\caption{Weights applied to individual facet temperature components in order to calculate complete and nadir temperatures for the Basel Sperrstrasse street canyon.}
	\label{weightings}
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}} p{1cm}p{1cm}p{1cm}p{1cm}p{1.6cm}}
		\toprule 
		& Road & Northwest & Southeast & Northwest & Southeast \\ 
		&  & Roof & Roof & Wall & Wall \\ 	\midrule
		Complete (T\textsubscript{comp}) & 0.33 & 0.16 & 0.16 & 0.16 & 0.16 \\ 
		Nadir (T\textsubscript{plan}) & 0.46 & 0.27 & 0.27 & 0.00 & 0.00 \\ 
		\bottomrule
	\end{tabular*} 
\end{table}

@@

The sheer number of unique path length geometries inherent with wide-FOV radiometry of urban areas makes full 3-dimensional radiative transfer simulation difficult and computationally intensive - particularly when correcting a long-term climatology of irradiances or T\textsubscript{hem, r}. In this method, to improve efficiency, radiances are calculated for azimuthally averaged path lengths that represent average surface-sensor geometry for each solid angle "slice" of the sensor FOV. Thus, hemispherical radiative transfer is reduced to a 2-dimensional problem as shown in Figure \ref{23radtran}. This greatly reduces the computational time required to model each irradiance - T\textsubscript{hem, r} pairing, as angular radiances can be computed as a function of zenith angle alone and subsequently weighted and integrated 3-dimensionally over the hemisphere.

To calculate surface-sensor geometries, the Surface-Sensor-Sun Urban Model (SUM) \citep{Soux2004} is initialized with a simplified, orthogonal 3-dimensional DBM representing surface geometry of the area surrounding the sensor. SUM uses a four-dimensional array to represent surface morphology with three spatial dimensions ($x$, $y$, and $z$), with $z$ representing height above the $x$, $y$ plane. An additional fourth dimension is used to store information describing each cell (in this case, distance from the point to the sensor). After specifying sensor position and FOV, the model determines which patches have an unobstructed line of sight to the sensor and calculates distance from "seen" patches to the sensor. Path lengths are binned at 5$^{\circ}$ increments of zenith angle and averaged to return an azimuthally-independent mean path length for each bin. In addition, while simulating path length geometries, SUM calculates view factors for each solid angle "slice", which are later used to weight 2-dimensional angular radiances in the hemispherical integration post-processing steps.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{23radtran}
	\caption{Path lengths over an urban surface. a) A downward radiometer mounted above a simplified three-dimensional urban surface showing b) the component radiances and path lengths from a vertical slice. Dotted lines indicate radiation streams subject to absorption by the intervening atmospheric layer.}
	\label{23radtran}
\end{figure}

@@

In this method, a "typical" longwave bandpass, approximately 250 - 2300 \si{\centi\meter^{-1}} (4 - 42 \si{\micro\meter}), was extended to include much smaller wavenumber (longer wavelengths). This was done for two reasons: 1) To accurately represent broadband spectral longwave emission curves, which show significant emittance in wavenumber smaller than 250 \si{cm^{-1}} (wavelengths much longer than 42 \si{\micro\meter}). 2) To replicate the spectral signal "seen" by a silicone-domed pyrgeometer, which continues to transmit radiation at wavenumber \textless 250 \si{cm^{-1}} (wavelengths \textgreater 42 \si{\micro\meter}). A "typical" longwave bandpass underestimates a pyrgeometer signal by approximately 7 - 10 \si{\watt\per\square\meter}, depending on emitter temperature. A comparison of ‘typical’ and ‘extended’ longwave bandpasses is shown in Figure \ref{dometrans}.

@@

\noindent where $ R(\lambda) $ is spectral radiance computed from a Planck function at an approximated emitter temperature and $r (\theta)$ is spectral sensor response.

@@

For a continuous 14-day period, profiles of up/downwelling short/longwave radiation, T\textsubscript{air}, and humidity measured from 2 \si{m}, 10 \si{m}, and 30 \si{m} were obtained from an instrumented tower in Payerne, Switzerland. The tower, installed over a cultivated field as a part of the Baseline Surface Radiation Network (BSRN), is located approximately 100 \si{\kilo\meter} southwest of the BUBBLE Sperrstrasse tower and is subject to similar summertime conditions as the study site. The study period was chosen to include a comprehensive range of T\textsubscript{surf}, T\textsubscript{air}, humidities, and cloud coverages to represent typical summertime conditions over which atmospheric corrections show the greatest variation. To evaluate the method, we used a modified version of the workflow described in Figure \ref{flow}. First, azimuthally averaged path lengths over a flat surface were calculated in SUM at 5\si{\degree} increments of zenith angle over the sensor FOV for the 10 \si{\meter} and 30 \si{\meter} sensors. For each time step, T\textsubscript{hem, b}, calculated from the lowest $L_z$ measurement, was used to model irradiances at 10 \si{m} and 30 \si{m} at 30 \si{\minute} intervals using concurrent profiles of T\textsubscript{air} and humidity. Daytime T\textsubscript{air} observed at the highest measurement level was anomalously high at all times of day compared to typical summertime lapse rates above flat vegetated terrain \citep{Oke1987}. This warm bias in T\textsubscript{air} measured at 30 \si{\meter} is observed even under high wind velocities, where one would expect little vertical difference in temperature not a strong temperature inversion. The fact that the observed warming bias remains constant over the 14-day study period prompted a slight modification to ensure the T\textsubscript{air} profile between 10 \si{\meter} and 30 \si{\meter} was representative of the neutral or weakly unstable daytime conditions and weakly stable nighttime conditions. It is likely that these modifications better represent the T\textsubscript{air} profile in the layer between 10 and 30 \si{\meter} than a simple interpolation between the 10 \si{\meter} T\textsubscript{air} measurement and the anomalously warm 30 \si{\meter} T\textsubscript{air} measurement. Contrary to the findings in \citet{Kotani2009a}, an isothermal atmospheric profile was not sufficient to accurately model upwelling fluxes over flat terrain. Although thermal stratification is relatively small by day in an urban canyon \citep{Nakamura1988} - where strong microscale contrasts in T\textsubscript{surf} foster strong canyon mixing and neutral stability - the large daytime T\textsubscript{surf} - T\textsubscript{air} differential and the path-length/transmittance gradient can create large differences in upwelling longwave forced by inter-canyon thermal contrasts - a phenomenon termed radiative divergence. By underestimating near-surface air temperatures and overestimating roughness-layer T\textsubscript{air}, daytime divergences are underestimated by an isothermal profile. As such, a full canyon T\textsubscript{air} and humidity profile is prefered to most accurately model near ground fluxes.

>>>>

TIR remote sensing of land surface temperature has emerged as a primary research focus in climatology, as researchers seek to better describe spatiotemporal patterns of T\textsubscript{surf} globally and better understand how anthropogenic modification of earth's surface influences land T\textsubscript{surf} and impacts climate at various scales. Over the last two decades, application of thermal remote sensing to study surface climates has expanded significantly. Thermal remote sensing of earth's surface has applications over a wide range of disciplines: from informing micro-, urban-, and global-scale climate models, to aiding decision making and mitigation praxis with respect to climate change and the urban heat island effect.

@@

Although most thermal remote sensors operate within one of the atmospheric windows - where atmospheric effects are minimal - virtually any remote sensed TIR signal is subject to radiative effects from the layer of atmosphere between the surface and the sensor. Over much of the thermal infrared waveband the atmosphere emits radiation and absorbs a fraction of radiation emitted by the surface. Thus, a remote sensed TIR signal is almost certainly not equal to the ground emitted signal. Spectral radiance received by a sensor at height ($z$) can be described by a function deviating from a Planck curve defined by T\textsubscript{surf} based on the spectral transmittance of the intervening atmosphere, with the magnitude of that deviation determined by the difference between Planck curves calculated from T\textsubscript{surf} and ambient T\textsubscript{air}. A radiative transfer code, such as MODTRAN \citep{Berk1987}, can be used to model the effect of the atmosphere on a remote sensed TIR signal. Radiative transfer simulations run in MODTRAN version 4.1 for two path lengths are shown in Figure \ref{spectairtsurf}, for spectral radiance emitted from a planar surface at 300 \si{\kelvin} through an isothermal atmosphere at 290 \si{\kelvin}, water vapor content of 12 \si{\gram\per\meter\cubed}, and aerosol and trace gas profiles from the mid-latitude summer standard atmosphere \citep{Kantor1962}. At both short and long path lengths, radiance in each band shows some deviation from the ground emitted signal. Larger deviations are observed at longer path lengths, where a significant portion of the resulting signal is emitted from the atmosphere, even in bands with high spectral transmittance. Long path lengths and a less transmissive atmosphere increase the potential for deviation in a remote sensed TIR signal from the ground emitted signal, while the difference between T\textsubscript{air} and T\textsubscript{surf} determines the resulting magnitude of atmospheric influence.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{spectairtsurf}
	\caption{At-sensor spectral directional radiances computed in MODTRAN 4.1 (Berk et al., 1987) for short (30 \si{m}) and long (3000 \si{m}) path lengths ($z$) with Planck curves indicating spectral radiances at T\textsubscript{surf} = 300 \si{K} and T\textsubscript{air} = 290 \si{K}.}
	\label{spectairtsurf}
\end{figure}

@@

Inversions of uncorrected $ L_z $ or \textbf{$L_z'$} yield a temperature equal to that of a blackbody emitting the same amount of radiation as detected by the sensor. Since $ L_z $ is unlikely to be equal to $ L_0 $ and, by extension,  $L_z'$ is unlikely to be equal to $L_0'$, T\textsubscript{hem, b} at $ z = 0 $ and T\textsubscript{hem, b} at $ z $ often show significant deviation. Hence, T\textsubscript{bright} and T\textsubscript{hem, b} are generally considered only a rough approximation representation of radiometric T\textsubscript{surf}.

@@

A large number of correction routines have been developed to remove atmospheric and emissivity effects from aerial and satellite TIR signals and derive accurate T\textsubscript{rad}. Methods range from simple mono-window \citep{Qin2001} and split-window \citep{Wan1996} routines for single-channel and multi-channel remote sensors, to schemes that integrate a radiative transfer code to isolate the surface emitted signal from interfering signals. Boundary conditions are standard across most correction methods: generally requiring vertical profiles of T\textsubscript{air}, humidity, pressure, and aerosol content to remove atmospheric effects, and surface radiative properties to correct for emissivity effects. However, correction methods are often instrument (or, at the very least, platform) specific and difficult to generalize across sensor and platform types. Few methods exist for correction of ground based remote sensed TIR --- none of which are robust enough to correct irradiances measured from a near-ground wide-field-of-view (FOV) radiometer mounted to view rough terrain.

@@

Several multi-LOS correction routines have been developed to remove atmospheric effects on near-ground remote sensed TIR: \citet{Meier2011} describes a correction method for oblique angled thermal imagery of urban terrain. In the method, spatially distributed LOS geometries were calculated by linking each image pixel to the corresponding 3-d coordinates of its viewpoint on a digital building model (DBM). Path lengths were then calculated as the distance between each pixel's corresponding location on the DBM and the sensor represented as the vanishing point of a 3-dimensional pyramidic projection from the sensor's location in the DBM. A pixel-by-pixel correction was then applied to remove atmospheric effects and retrieve T\textsubscript{rad} for each pixel at 30 minute intervals, resulting in a brief, time-continuous climatology of urban T\textsubscript{rad}. However, the method uses thermal images in conjunction with a DBM to calculate path length geometries for each pixel's LOS - a technique not possible with a pyrgeometer, which returns a single integrated value over the sensor FOV. Moreover, the target instrument operates over a narrow waveband with relatively uniform spectral sensor response, reducing the magnitude and variance in atmospheric transmission over the sensor response curve. Thus, the method is not directly generalizable to correct TIR measured via pyrgeometer.

\citet{Kotani2009a} describes a method for correction of wide-FOV (pyrgeometer) TIR irradiances over a homogeneous planar surface. In this method, path lengths were calculated for six sensor heights. Radiances were then modeled using the LOWTRAN \citep{Kneizys1988} radiative transfer code initialized at $5^{\circ}$ intervals and integrated over the hemisphere to retrieve irradiances for a suite of T\textsubscript{surf}, and ambient T\textsubscript{air} and humidities. The resulting lookup table (LUT) of values is then used to correct $L_z$ and quantify atmospheric effects on remote sensed $L_z$ measured from several sensor heights.

The two existing methods are limited to narrow-FOV thermal imagers and planar terrain respectively. Thus, for atmospheric correction of TIR upwelling from urban terrain measured via downward facing pyrgeometer a method which combines \citet{Meier2011}'s representation of complex surface geometry and \citet{Kotani2009a}'s broadband hemispherical integration is needed.

@@

The "rolling lookup-table" method described in this study uses a sensor view model in conjunction with a radiative transfer code to model hemispherical irradiances upwelling from a simplified isothermal 3-dimensional representation of the urban surface. In summary, the method (depicted in Figure \ref{flow}) uses vertical profiles of measured T\textsubscript{air} and humidity to model at-sensor spectral radiances at 5$^{\circ}$ increments over the sensor FOV for a predetermined range of possible T\textsubscript{hem, r} at each time-step. Spectral directional radiances are convolved by a dome transmittance curve, integrated over the sensor waveband, and weighted for their respective angular view factor. Weighted directional radiances are then integrated over the hemisphere and aggregated into a LUT of modeled irradiance - T\textsubscript{hem, r} pairings for each time step, unique to the vertical profile of measured T\textsubscript{air} and humidity. Finally, for each time step, measured irradiances are matched with the closest modeled irradiances in the LUT to return an atmospherically corrected radiometric hemispherical surface temperature. This process is repeated at 30 minute intervals to yield a continuous climatology of urban T\textsubscript{hem, r}. The following sections introduce the study area for which the method was developed and describe the sensor view model, radiative transfer, and post-processing steps of the correction method.

@@

With methodological generalizability in mind, a "rolling lookup table" atmospheric correction method was developed to retrieve radiometric T\textsubscript{hem, r} for a climatology of upwelling longwave irradiances measured from above the Sperrstrasse street canyon in Basel, Switzerland. The site, instrumented as a part of the Basel Urban Boundary Layer Experiment (BUBBLE) \cite{Rotach2005}, has an approximately northeast-southwest orientation and site morphology representative of local climate zone (LCZ) 2\footnote{Site surroundings can be described by the following morphological parameters: mean building height: 14.6m, plan aspect ratio: 0.54, complete aspect ratio: 1.92, local canyon aspect ratio: 1.0, and average shortwave albedo: 0.11 \cite{Rotach2005}.} \cite{Stewart2012}. LCZ classification was based on an assessment of surface characteristics in a 250 \si{\meter} circular area extending from the Sperrstrasse tower using a 1 \si{m} raster digital building model (DBM). Thus, the morphological parameters identified in \cite{Rotach2005} are representative of a majority of the pyrgeometer footprint. Vegetation was not included in the DBM, and is not represented in morphological assessment or the sensor view model, however, the street canyon and surrounding area has little vegetation.

For the eight month period between December 2001 and July 2002, a triangular lattice tower was installed within the Sperrstrasse street canyon. Its location was skewed towards the southeast facing wall near the along-canyon center of the canyon. Instruments to observe a full suite of meteorological variables and fluxes of heat, mass, and momentum are mounted at various levels on the tower. Profiles of T\textsubscript{air} and humidity were measured at seven heights extending from 2.5 \si{m} to 31.5 \si{m} above the canyon floor (with the highest observation level at approximately 2.17 times mean roof level). Upwelling and downwelling short/longwave fluxes were obtained from radiometers mounted at the lowest and highest measurement levels, with an additional downward facing pyrgeometer mounted at roof level near the center of the street canyon. In addition, during a summertime intensive observation period (IOP) an array of narrow-FOV IRTs was installed to sample representative individual facet surface temperatures (T\textsubscript{facet}).

The BUBBLE Sperrstrasse site was chosen here for two primary reasons: 1. The site provided a long-term climatology of radiation and meteorological variables for a representative mid-latitude city. This allowed for examination of urban T\textsubscript{surf}, sUHI, and atmospheric correction magnitudes over a wide range of representative mid-latitude conditions. 2.  Inclusion of T\textsubscript{facet} over the IOP allows for investigation of the effect of sensor FOV and viewing direction on remote sensed urban T\textsubscript{surf} for common methods for urban T\textsubscript{surf} retrieval. This directional dependence of urban T\textsubscript{surf} - termed "effective anisotropy" - refers to the notion that a remote sensed TIR signal can vary based on the combined effects of surface-sensor-sun geometry and the convoluted, 3-dimensional structure of the urban surface \cite{Voogt1998a}. Facet surface temperatures measured during the summertime IOP allow for direct climatological comparison of T\textsubscript{hem, r} to common remote sensed representations of the urban surface calculated from weighted averages of wall (T\textsubscript{wall}), road (T\textsubscript{road}), and roof (T\textsubscript{roof}) temperatures. Plan and complete aspect ratios are used to derive weightings for nadir remote sensed (T\textsubscript{plan}) and complete (T\textsubscript{comp}) representations of urban surface temperature - described in Table \ref{weightings}. T\textsubscript{comp} represents a complete urban T\textsubscript{surf}, where facet temperatures are averaged based on their proportion of the complete urban surface area, while T\textsubscript{plan} represents the Sperrstrasse site as viewed by a narrow-FOV remote sensor in the nadir. To facilitate comparison over the IOP, T\textsubscript{hem, r} and T\textsubscript{plan} were divided by T\textsubscript{comp} and averaged over the IOP to yield normalized mean T\textsubscript{hem, r} and T\textsubscript{plan} at 30-minute intervals. Through comparison of T\textsubscript{hem, r} to T\textsubscript{plan} and T\textsubscript{comp} we investigate the effect of sensor-surface geometry on remote sensed urban T\textsubscript{surf} and quantify directional biases in common urban T\textsubscript{surf} measurements.

\begin{table}[H]
	\centering
	\caption{Weights applied to individual facet temperature components in to calculate complete and nadir temperatures for the Basel Sperrstrasse street canyon.}
	\label{weightings}
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}} p{1cm}p{1cm}p{1cm}p{1cm}p{1.6cm}}
		\toprule 
		& Road & Northwest & Southeast & Northwest & Southeast \\ 
		&  & Roof & Roof & Wall & Wall \\ 	\midrule
		Complete (T\textsubscript{comp}) & 0.33 & 0.16 & 0.16 & 0.16 & 0.16 \\ 
		Nadir (T\textsubscript{plan}) & 0.46 & 0.27 & 0.27 & 0.00 & 0.00 \\ 
		\bottomrule
	\end{tabular*} 
\end{table}

@@

The sheer number of unique path length geometries inherent with wide-FOV radiometry of urban areas makes full 3-dimensional radiative transfer simulation difficult and computationally intensive - particularly when correcting a long-term climatology of irradiances or T\textsubscript{hem, r}. In this method, to improve efficiency, radiances are calculated for azimuthally averaged path lengths that represent average surface-sensor geometry for each solid angle "slice" of the sensor FOV. Thus, hemispherical radiative transfer is reduced to a 2-dimensional problem similar to that shown in Figure \ref{23radtran}. This greatly reduces the computational time required to model each irradiance - T\textsubscript{hem, r} pairing, as angular radiances can be computed as a function of zenith angle alone and subsequently weighted and integrated 3-dimensionally over the hemisphere.

To calculate surface-sensor geometries, the Surface-Sensor-Sun Urban Model (SUM) \citep{Soux2004} is initialized with a simplified, orthogonal 3-dimensional DBM that represents surface geometry of the surrounding area. SUM uses a four-dimensional array to represent surface morphology with three spatial dimensions ($x$, $y$, and $z$), with $z$ representing height above the $x$, $y$ plane. An additional fourth dimension is used to store information describing each cell (in this case, distance from the point to the sensor). After specifying sensor position and FOV, the model determines which patches have an unobstructed line of sight to the sensor and calculates distance from "seen" patches to the sensor. Path lengths are binned at 5$^{\circ}$ increments of zenith angle and averaged to return an azimuthally-independent mean path length for each bin. In addition, while retrieving path length geometries, SUM calculates view factors for each solid angle "slice", which are later used to weight angular radiances in the hemispherical integration post-processing steps.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{23radtran}
	\caption{Path lengths over an urban surface. Left: a downward radiometer mounted above a simplified three-dimensional urban surface (Left) and the component radiances and path lengths from a vertical slice (Right). Dotted lines indicate radiation streams subject to absorption by the intervening atmospheric layer.}
	\label{23radtran}
\end{figure}

@@

In this method, a "typical" longwave bandpass, approximately 250 - 2300 \si{\centi\meter^{-1}} (4 - 42 \si{\micro\meter}), was extended to include much smaller wavenumber (longer wavelengths). This was done for two reasons: 1) To accurately represent broadband spectral longwave emission curves, which show significant emittance in wavenumber smaller than 250 \si{cm^{-1}} (wavelengths longer than 42 \si{\micro\meter}). 2) To replicate the spectral signal "seen" by a silicone-domed pyrgeometer, which continues to transmit radiation at wavenumber \textless 250 \si{cm^{-1}} (wavelengths \textgreater 42 \si{\micro\meter}). A "typical" longwave bandpass underestimates a pyrgeometer signal by approximately 7 - 10 \si{\watt\per\square\meter}, depending on emitter temperature. A comparison of ‘typical’ and ‘extended’ longwave bandpasses is shown in Figure \ref{dometrans}.

@@

\noindent where $ R(\lambda) $ is spectral radiance computed from a Planck function at an approximated emitter temperature and $r (\lambda)$ is spectral sensor response.

@@

For a continuous 14-day period, profiles of up/downwelling short/longwave radiation, T\textsubscript{air}, and humidity measured from 2 \si{m}, 10 \si{m}, and 30 \si{m} were obtained from an instrumented tower in Payerne, Switzerland. The tower, installed over a cultivated field as a part of the Baseline Surface Radiation Network (BSRN), is located approximately 100 \si{\kilo\meter} southwest of the BUBBLE Sperrstrasse tower and is subject to similar summertime conditions as the study site. The study period was chosen to include a comprehensive range of T\textsubscript{surf}, T\textsubscript{air}, humidities, and cloud coverages to represent typical summertime conditions over which atmospheric effects on TIR can vary significantly. To evaluate the method, we used a modified version of the workflow described in Figure \ref{flow}. First, azimuthally averaged path lengths over a flat surface were calculated in SUM at 5\si{\degree} increments of zenith angle over the sensor FOV for the 10 \si{\meter} and 30 \si{\meter} sensors. For each time step, T\textsubscript{hem, b} calculated from the lowest $L_z$ measurement was used to model irradiances at 10 \si{m} and 30 \si{m} at 30 \si{\minute} intervals using concurrent profiles of T\textsubscript{air} and humidity. Daytime T\textsubscript{air} observed at the highest measurement level was anomalously high compared to typical summertime lapse rates above flat vegetated terrain \citep{Oke1987}. This warm bias in T\textsubscript{air} measured at 30 \si{\meter} is observed even under high wind velocities, where one would expect little vertical difference in temperature and certainly not a strong temperature inversion. The fact that the observed warming bias remains relatively constant over the 14-day study period prompted a slight modification to ensure the T\textsubscript{air} profile between 10 \si{\meter} and 30 \si{\meter} was representative of the neutral or weakly unstable daytime conditions. It is likely that these modifications better represent the actual T\textsubscript{air} profile in the layer between 10 \si{\meter} and 30 \si{\meter} than a simple interpolation between the 10 \si{\meter} T\textsubscript{air} measurement and the anomalously warm 30 \si{\meter} T\textsubscript{air} measurement.

Contrary to the findings in \citet{Kotani2009a}, an isothermal atmospheric profile was not sufficient to accurately model upwelling fluxes over flat terrain. Although thermal stratification is relatively small by day in an urban canyon \citep{Nakamura1988} --- where strong microscale contrasts in T\textsubscript{surf} foster strong canyon mixing and neutral stability --- the large daytime T\textsubscript{surf} - T\textsubscript{air} differential and the path length/transmittance gradient can create large differences in upwelling longwave forced by inter-canyon thermal contrasts - a phenomenon termed radiative divergence. By underestimating near-surface T\textsubscript{air} and overestimating roughness-layer T\textsubscript{air}, daytime divergences are underestimated by an isothermal profile. As such, a full canyon T\textsubscript{air} and humidity profile is preferred to most accurately model near ground fluxes.
